Bird beak's elaboration and exploration

### 2022-06-14 Analysis/02-mcmcmcglmmm_analysis.Rmd
Update 02-mcmcmcglmmm_analysis.Rmd

## Loading the parametrisation data
load(file = "../Data/Processed/shapespace_passeriformes_suborder_family.rda")

## Select the data
shapespace <- shapespace_passeriformes_suborder_family[[1]]$space
selected_dim <- shapespace_passeriformes_suborder_family[[1]]$dimensions
consensus_tree <- shapespace_passeriformes_suborder_family[[1]]$consensus_tree
trees_list <- shapespace_passeriformes_suborder_family[[1]]$trees_list
```

@@

# Running the three MCMCglmm models
save(param_chains, file = "../Data/Processed/params_shapespace_8D_50levels_50k_chain1.rda")
```

>>>>

## Loading the parametrisation data
load(file = "../Data/Processed/shapespace_passeriformes_two_levels.rda")

## Select the data
shapespace <- shapespace_passeriformes_two_levels[[1]]$space
selected_dim <- shapespace_passeriformes_two_levels[[1]]$dimensions
consensus_tree <- shapespace_passeriformes_two_levels[[1]]$consensus_tree
trees_list <- shapespace_passeriformes_two_levels[[1]]$trees_list
```

@@

# Running the three MCMCglmm models
save(param_chains, file = "../Data/Processed/params_passerines_shapespace_8D_28levels_50k.rda")
```
